Scheeper's Meager-NWD Game and the Menger Game

### 2015-01-30 phd/dissertation/chapter2.tex
fixes suggested by Dr. Rodger

\begin{defn}
  A \term{game} is a tuple $\<M,W\>$ such that
  $W\subseteq M^{\omega}$. $M$ is set of \term{moves} for
  the game, and $M^{\omega}$ is the set of all possible
  \term{playthroughs} of the game.

@@

Intuitively, a strategy is a rule for one of the players on how to play
the game based upon the previous (finite) moves of her opponent, while an
attack is a fixed strike by an opponent indexed by round number.

@@

We now may rigorously define the notion of ``forcing'' a win in a game.

@@

\begin{defn}
  If a winning $k$-tactical strategy exists for a player $\pl A$ in the game
  $G$, then we write $\pl A \ktactwin{k} G$. If $k=1$, then $\pl A \tactwin G$.

  If a winning $k$-Markov strategy exists for a player $\pl A$ in the game
  $G$, then we write $\pl A \kmarkwin{k} G$. If $k=1$, then $\pl A \markwin G$,
  and if $k=0$, then $\pl A \prewin G$.
\end{defn}

@@

\begin{defn}
  $X$ is an \term{$\alpha$-favorable space}
  when $\pl N \tactwin \bmgame{X}$.
  $X$ is a \term{weakly $\alpha$-favorable space}
  when $\pl N \win \bmgame{X}$.
\end{defn}

>>>>

\begin{defn}
  A \term{game} is a tuple $\<M,W\>$ such that
  $W\subseteq M^{\omega}$. $M$ is the set of \term{moves} for
  the game, and $M^{\omega}$ is the set of all possible
  \term{playthroughs} of the game.

@@

Intuitively, a strategy is a rule for one of the players on how to play
the game based upon the previous (finite) moves of the opponent, while an
attack is a fixed strike by an opponent indexed by round number.

@@

We now rigorously define the notion of ``forcing'' a win in a game.

@@

\begin{defn}
  If a winning $k$-tactical strategy exists for a player $\pl A$ in the game
  $G$, then we write $\pl A \ktactwin{k} G$. If $k=1$, then
  we may write $\pl A \tactwin G$.

  If a winning $k$-Markov strategy exists for a player $\pl A$ in the game
  $G$, then we write $\pl A \kmarkwin{k} G$. If $k=1$, then we may write
  $\pl A \markwin G$;
  if $k=0$, then we may write $\pl A \prewin G$.
\end{defn}

@@

\begin{defn}
  $X$ is said to be an \term{$\alpha$-favorable space}
  when $\pl N \tactwin \bmgame{X}$.
  $X$ is said to be a \term{weakly $\alpha$-favorable space}
  when $\pl N \win \bmgame{X}$.
\end{defn}
